At the beginning of the project we were given a problem to design a solution for. The problem was that in many
circumstances, a whole bunch of people have to stay together in the same place for a considerable amount of
time. Often, however, these people do not even know each other, but they still stay together at the same location. A game would make some of these situations bearable, e.g. when there is waiting time involved. After playing a game in such a situation it can also give the user a sense of e.g. achievement when a user gets a new high score or solves a difficult puzzle. \\
For our project we were assigned to design a game to entertain such large groups of people and fulfill our end-user's need. The requirements from the end-user were that the game must be original, i.e. the game concepts must be unique. The game must also be creative, fun to play and also let people interact with each other through e.g. verbal communication with each other. \\
As a solution to this context problem we developed a game called Taxi Trouble and it will be introduced in the next chapter. \\
\newline
This document is about the developed, implemeted and validated software product. In Chapter 2 it will provide an overview of developed and implemented software product. Chapter 3 will describe the developed functionalities. An HCI module that was realized for the user interaction with the developed solution is provided in Chapter 4.  In Chapter 5 an evaluation of the functional modules and the product in its entirety, including the failure analysis will be provided. And at the end of the document in Chapter 6 an outlook will be provided regarding the possible improvements in the future and the strategy to achieve these improvements.
