For the past nine weeks our game development team has been developing a competitive, cooperative and interactive computer game designated with the name Taxi Trouble. In this chapter an overview is given of the developed product and its implemented functionalities. A more elaborate description of the functionalities of the game is given in the succeeding chapter.
\\*
The game Taxi Trouble is a game which can be played together by 4 to 8 players at the same time. The game is played on an Android device and uses the Google Play Game Services to allow people to connect with each other and play a game with each other. A player can select the amount of players that he or she wants to play a game with after which a waiting room is initiated. When all players are connected, the game starts and teams are formed randomly. Each team consists of two players where one gets the role of taxi-driver and the other gets the role of navigator. The taxi-driver of each team drives around in a large city and has only a limited view of the city. Therefore the role of navigator is introduced that has a complete overview of the citymap and needs to guide its partner to the right locations. For a team to win the game the players need to communicate very well to get the highest score when the time limit has exceeded.
\\*
When the game starts the main menu of the game is shown in which the player can choose to either press the start button for starting a new game or the leaderboard button to check out the leaderboard.
To start a game the player logs in with his/her Google Account and chooses the amount of players with which the player wants to play. Also a player can invite other players with their Google Account. When everyone has joined the game the game starts and the roles are divided.
As explained earlier each team consists of a taxi-driver and navigator which have to communicate very well to win the game. Each driver has a taxi which he or she can steer and accelerate. For the team to score points there are passengers in the game which can be picked-up by a taxi and afterwards dropped off with a certain time-limit at its destination. As well taxis can steal passengers from each other while bringing them to their destination. Also for a team to increase their chance to win the game there are power-ups in the city that can be picked up by the team's taxi and later on activated by a navigator. Further sound effects are being played when certain events in the game occur. Finally a head-up display(hud) is displayed on screen to show game state info like the team score, timer and team identifier. When the game ends each team's final score is submitted to the leaderboard.