
\documentclass[a4paper, answers,fleqn]{exam}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{tkz-graph}
\usepackage[lined,commentsnumbered]{algorithm2e}
\usepackage{amssymb}
\usepackage{amsmath,amsthm}
\usepackage{amsfonts}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{qtree}
\usepackage{pgf}
\usepackage{tikz}
\usepackage[latin1]{inputenc}
\usepackage{bm}

\begin{document}
\begin{itemize}
	\item Mysterious map that can increase concentration on the navigator
	\item The match must be based on accomplishment of a mission such as completing a route or getting a special item in the map. the item can be limited so the person who gets to the item location is a winner and become the only winner
	\item If there is some behavior that allow participants to violate the driving rule will make the game more interesting.
	\item The top view is more handy for the driver
	\item Excitment of  the navigator must be considered equally as driver, my Idea is to always let navigator to make the strategy of how to complete the mission.
	\item The people who are participating can have a option to choose to be a driver or navigator
	\item Speed of the race must be controlled automatically so the focus be more on completing a mission and also to focus on direction handling.
	\item Game menu should include an quick tutorial 
	\item If the team win they will go to a higher ranking, and particpants can have a perfect matching sorted on their points.
	\item There is an special gift like powers,booster,ghost car,etc. for the car somewhere in the map with a certain amount of points neede to unlock.
	\item aPrticpant can spend their points on the gifts.

\end{itemize}
\end{document}