
% In this section the needs of the customers that the product addresses are identified. The project mainly
% addresses the need of large group of people to have a form of entertainment while waiting. This should
% 1
% be accomplished while making the people that are present communicate with each other as much as
% possible. The product does this by making people interact and cooperate with each other, but as well
% compete against each other at the same time. Further the product ensures that the users can start
% playing the game without a time-consuming setup or a long time to learn the rules of the game. It as
% well does not require more than a smart device that most people own nowadays. Finally the game should
% not consume to much time from the customer, which means it should be easy to get to know the rules
% of the game and as well each game should finish in several minutes.

In this section explanation is given for the customer needs that this game product will fulfill. The game is designed to entertain either large or small group of people who are waiting for a short period of time in a common place. When a person plays a game he or she is mostly looking forward to experience a sense of competitiveness, interaction and collaboration. This game has been designed to consider all those needs but moreover to make the player be completely engaged while playing the game. The product ensures that the users can start playing the game without a time-consuming setup or a long time to learn the rules of the game. It as well does not require more than a smart device that most people own nowadays. 
 \subsection{Basic Needs}

 The basic needs of the target customer needs are fullfilled by playing this interactive multi-player game, These basic needs are as follows:
 \begin{itemize}
   	\item Gaining knowledge of map reading and navigation.
   	\item Gaining and improving their skills.
   	\item Feeling competent.
   	\item Preserving through hard times.
   	\item Managing danger.
   	\item Competing for rewards.
   	\item Cooperating for rewards.
   	\item Satisfying the senses with pleasant inputs such as sights ,sounds , etc.
   	\item Gaining a sense of responsibility towards their partner.
\end{itemize}  


     