Cairns, P., Cox, A. L., Day, M., Martin, H., and Perryman, T. (2013). Who but not where: The effect of social play on immersion in digital games. International Journal of Human-Computer Studies.
\vspace{0.15cm}\\
Ducheneaut, N. and Moore, R. J. (2004). The social side of gaming: a study of interaction patterns in a massively multiplayer online game. In Proceedings of the 2004 ACM conference on Computer supported cooperative work, CSCW '04, pages 360-369, New York, NY, USA. ACM.
\vspace{0.15cm}\\
Granic, I., Lobel, A. and Engels, R. C. M. E. (2013), The Benefits of Playing Video Games. Radboud University. Nijmegen, NL.
\vspace{0.15cm}\\
Gajadhar, B. J., Kort, Y. A. W., and IJsselsteijn, W. A. (2008). Shared fun is doubled fun: Player enjoyment as a function of social setting fun and games. In Markopoulos, P., Ruyter, B., IJsselsteijn, W., and Rowland, D., editors, Fun and Games, volume 5294 of Lecture Notes in Computer Science, chapter 11, pages 106-117, Springer Berlin / Heidelberg, Berlin, Heidelberg.
\vspace{0.15cm}\\
Khaled, R., Barr, P., Johnston, H. and Biddle, R. (2009). Let's clean up this mess: exploring multi-touch collaborative play. In D. R. O. Jr., R. B. Arthur, K. Hinckley, M. R. Morris, S. E. Hudson and S. Greenberg (eds.), CHI Extended Abstracts, pages 4441-4446, Boston, MA, USA, 2009. ACM. ISBN: 978-1-60558-247-4
\vspace{0.15cm}\\
Sellar, T. (2004). User experience in interactive computer game development. In Computer Human Interaction, pages 675-681.
\vspace{0.15cm}\\
Vorderer, P., Hartmann, T., and Klimmt, C. (2003). Explaining the enjoyment of playing video games: the role of competition. In Proceedings of the second international conference on Entertainment computing, ICEC '03, pages 1-9, Pittsburgh, PA, USA. Carnegie Mellon University.
\vspace{0.15cm}\\
Yan, R.N. and Lotz, S. (2006). The Waiting Game: The Role of Predicted Value, Wait Disconfirmation, and Providers' Actions in Consumers' Service Evaluations. In NA - Advances in Consumer Research, Volume 33, eds. Pechmann, C. and Price, L., pages 412-418, Duluth, MN, USA, ACR.


